Ant Cuticle Texture Classification Algorithm for Ecological Anaylsis

### 2022-06-01 paper/main.tex
update abstract

\begin{abstract}
    Definition modeling, the task of generating a definition for a given term,
    is a relatively new area of research applied in evaluating word embeddings.
    Automatic generation of dictionary quality definitions has many applications
    in natural language processing, such as sentiment analysis, machine
    translation, and word sense disambiguation. Additionally, definition
    modeling is also helpful for evaluating the quality of word embeddings. As
    more research is done in this field, the need for a summary of different
    applications, approaches, and obstacles grows apparent. This review provides
    an overview of the current research in definition modeling and a list of
    future directions and trends.
\end{abstract}
\keywords{texture analysis; image processing; clustering; machine learning; ecology}
\maketitle

>>>>

\begin{abstract}
    There is a large variety of ant species, and most species are diverse in
    terms of size, shape, behaviors, and especially cuticle textures. However,
    the significance of ant cuticle texture is not widely researched. Ant
    cuticle texture presumably provides some type of function, and therefore is
    useful to research for ecological applications and bioinspired designs. This
    research employs modern machine learning methods such as texture analysis
    and deep machine learning to automatically group similar ant species based
    on morphological traits. We provide a comparative study of the performance
    of modern texture analysis methods on ant head images. We evaluate the
    results of the classification methods with modern visualization techniques.
\end{abstract}
\keywords{texture analysis; image processing; clustering; machine learning; ecology}
\maketitle
